\nocite{*}
\bibliographystyle{gost780u}
\begin{thebibliography}{9}
    \bibitem{tsai} Tsai, T. (2016). Audio Hashprints: Theory \& Application.
    (Doctoral dissertation, EECS Department, University of California, Berkeley).

    \bibitem{chromaprint}
    Yan Ke, Derek Hoiem, Rahul Sukthankar. (2005). Computer Vision for Music
    Identification, Proceedings of Computer Vision and Pattern Recognition.

    \bibitem{hnsw} Leonid Boytsov and Bilegsaikhan Naidan (2013).
    Engineering Efficient and Effective Non-metric Space Library.
    In Similarity Search and Applications - 6th International Conference, SISAP 2013,
    A Coru\~na, Spain, October 2-4, 2013, Proceedings (pp. 280–293). Springer.

    \bibitem{essentia} Bogdanov, D., Wack N., Gómez E., Gulati S., Herrera P., Mayor O., et al. (2013).
    ESSENTIA: an Audio Analysis Library for Music Information Retrieval. International Society for Music Information Retrieval Conference (ISMIR'13). 493-498.

    \bibitem{cqt} Schörkhuber, C., Klapuri, A., Holighaus, N., \& Dörfler, M. (n.d.).
    A Matlab Toolbox for Efficient Perfect Reconstruction Time-Frequency Transforms with Log-Frequency
    Resolution

    \bibitem{eigen} Gael Guennebaud, Benoit Jacob, \& others. (2010). Eigen v3.

    \bibitem{tf} T. Huang, C. Lin, G. Guo and M. Wong, "Cpp-Taskflow: Fast Task-Based Parallel
    Programming Using Modern C++," 2019 IEEE International Parallel and Distributed Processing
    Symposium (IPDPS), Rio de Janeiro, Brazil, 2019, pp. 974-983, doi: 10.1109/IPDPS.2019.00105.
\end{thebibliography}